Analyzing Information Transfer from Different Data Sources via Precise Bias-variance Asymptotics

### 2021-07-03 revision_journal/setup.tex
Updates from Overleaf

\begin{lemma}[Variance asymtotics of OLS estimators, cf. Theorem 2.4 of \citet{isotropic} and Theorem 3.14 of \citet{DY}]\label{fact_tr}
	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
	Under Assumption \ref{assm_big1}, we have that for any deterministic $p\times p$ matrix $\Sigma$,
		\[ \bigtr{\Sigma \frac1{(X^{(2)})^\top X^{(2)} }  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  }
		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|A\| \right) \]
		with high probability for any small constant $\e>0$.
\end{lemma}
 %The above result has a long history in random matrix theory.
If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for %the mean of
the inverse Wishart distribution \citet{anderson1958introduction}. For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}). Here we have presented the results from \citet{isotropic} and \citet{DY}, who give an almost sharp convergence rate.

>>>>

\begin{lemma}[Variance asymtotics of OLS estimators, cf. Theorem 2.4 of \citet{isotropic} and Theorem 3.14 of \citet{DY}]\label{fact_tr}
	%Let $X  \in \real^{n\times p}$ be a random matrix that satisfies Assumption \ref{assume_rm}.
	%Let $\Sigma\in\real^{p\times p}$ denote the population covariance matrix of $X$.
	Under Assumption \ref{assm_big1}, we have that for any deterministic $p\times p$ matrix $\Sigma$,
		\[ \bigtr{\Sigma \frac1{(X^{(2)})^\top X^{(2)} }  } %= \bigtr{ \frac1{(Z^{(2)})^\top Z^{(2)} }  }
		= \frac{1}{n_2 - p}\bigtr{\Sigma (\Sigma^{(2)})^{-1}} +  \OO\left( \frac{p^{\e}}{\sqrt{n_2 p}}\cdot \frac{p}{n_2}\|\Sigma\|_{op} \right) \]
		with high probability for any small constant $\e>0$.
\end{lemma}
\todo{the scaling $\sqrt{n_2}$ above doesn't seem correct}

 %The above result has a long history in random matrix theory.
If the entries of $Z^{(2)}$ are i.i.d. Gaussian, then this result follows from the classical result for %the mean of
the inverse Wishart distribution \citet{anderson1958introduction}. For a general non-Gaussian $Z^{(2)}$, this result can be obtained using the well-known Stieltjes transform method (cf. Lemma 3.11 of \citet{bai2009spectral}). Here we have presented the results from \citet{isotropic} and \citet{DY}, who give an almost sharp convergence rate.
